Draft_markdown_v1

### 2024-04-12 Draft_V1.Rmd
Update Draft_V1.Rmd

---
title: "Draft_markdown_v1"
author: "River Kim"
date: "2024-04-07"
output:
  html_document: default
  word_document: default
---

@@

```{r}
library(tidyverse)
library(readr)
library(tidytext)
library(quanteda)
library(textdata)
```

@@

tidy_data_notoken %>%
  group_by(party) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

@@

```{r}
# Plotting counts of immigration texts by party
ggplot(text_count, aes(x = Year, y = n, group = party, color = party)) +
  geom_line() +
  labs(y = "Immigration texts num", x = "Year") +
  scale_x_continuous(breaks = seq(min(text_count$Year), max(text_count$Year), by = 4))
  theme_minimal()
```

@@

```{r}
#Plotting the ratios
ggplot(filtered_ratio_count, aes(x = Year, y = ratio, group = party, color = party)) +
  geom_line() +
  labs(y = "% Immigration Texts (n>100)", x = "Year") +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0), limits = c(0, NA)) +
  scale_x_continuous(breaks = seq(min(filtered_ratio_count$Year), max(filtered_ratio_count$Year), by = 4)) +
  theme_minimal()
```

@@

tidy_data <- tidy_data %>%
  arrange(date)
tidy_data$order <- 1:nrow(tidy_data) # Make orders of each word
```

@@

# Make nrc sentiment tables of data
nrc_data <- tidy_data %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  count(date, index = order %/% 1000, sentiment) %>%
  spread(key = sentiment, value = n, fill = 0) %>%
  mutate(ratio = negative / (positive+1)) # Calculating negative/positive ratio. Adding 1 to avoid the 0 denominator

@@

```{r}
# Total sentiment of text including immigration related words plot
nrc_data %>%
  ggplot(aes(date, ratio)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", alpha=0.5) +
  labs(y = "Total NRC sentiment negative ratio", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red") +
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
```

@@

```{r}
# A negative sentiment ratio plot of four parties
filtered_nrc_data_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.5, size = 1) +
  geom_smooth(method="loess", se = F, alpha=0.7, size = 1) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(y = "NRC Sentiment Negative Ratio by Party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red", size = 1) +
  annotate("text", x = as.Date("2007-09-24"), y = 4, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r}
# Faceting by party
filtered_nrc_data_party %>%
  ggplot(aes(x = date, y = ratio, color = party)) +
  geom_point(alpha = 0.5, size = 2) +
  geom_smooth(method = "loess", se = FALSE, alpha = 0.7, size = 1) +
  labs(y = "NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

show(dominant_senti_nrc_party)
```

@@

```{r}
# Plotting specific sentiment changes by party
long_nrc_data %>%
  ggplot(aes(x = date, y = score, color = sentiment)) +
  geom_smooth(method = "loess", se = F, alpha = 1, size = 1) +
  geom_point(alpha = 0.5, size = 0.5) + 
  facet_wrap(~ party, scales = "free_y") +
  labs(x = "Date", y = "Score") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

# Plots of specific negative sentiments by party 
long_nrc_data_neg %>%
  ggplot(aes(x = date, y = score, color = sentiment_negative)) +
  geom_smooth(method = "loess", se = F, alpha = 0.75, size = 1) +  
  geom_point(aes(shape = sentiment_negative), alpha = 0.5, size = 1) + 
  facet_wrap(~ party, scales = "free_y", nrow = 2) + 
  labs(x = "Date", y = "Score") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

## 5) Random sample sentiment

@@

# Applying NRC dictionary and calculating total negative ratio
samp_nrc_data <- tidy_samp %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  count(date, index = order %/% 1000, sentiment) %>%
  spread(key = sentiment, value = n, fill = 0) %>%
  mutate(ratio = negative / (positive+1))

@@

```{r}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) + 
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r}
# Faceting plots by party
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = F, alpha = 0.7, size = 1) +
  labs(y = "Sample NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

```{r}
# choice parameters
WINDOW_SIZE <- 6 # context up to 6 words
DIM <- 300 # the length of the word vector
ITERS <- 100 # the maximum number of iterations
COUNT_MIN <- 10 # minimum count of words

@@

```{r}
#set model parameters
glove <- GlobalVectors$new(rank = DIM, x_max = 100, learning_rate = 0.05)

@@

Plot the total word embedding of 'immigration' with the GloVe model generated above

@@

The ggplot visual for GloVe

```{r}
ggplot(selected_words, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "GloVe word embedding of words related to 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_2, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Total parliament immigration related speech word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylums)
word_3 <- glove_embedding["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding, y = word_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_3 <- df_glove_umap %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_3, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Total parliament immigration related speech word embedding of words related to *asylum*

@@

```{r}
# filter data by date. Now have pre/post economic crisis text data related to immigration.

@@

```{r}
set.seed(42L)
glove_text_pre <- sample(data_pre$desc)

@@

```{r}
url_pre <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_pre.rds?raw=true"
golve_embedding_pre <- readRDS(url(url_pre, method = "libcurl"))
```

@@

```{r}
ggplot(df_umap_pre) +
  geom_point(aes(x = Pre_UMAP1, y = Pre_UMAP2), color = 'blue', size = 0.05) +
  labs(title = "(Pre-crisis) GloVe word embedding of words related to 'immigration'") +
  theme_minimal()
```

@@

Pre-crisis total parliament speech word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylums)
word_pre_3 <- glove_embedding_pre["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_pre, y = word_pre_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_pre_3 <- df_umap_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_3, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
# Plot the word embedding of words that are related for the GloVe model (asylum)
word_pre_4 <- glove_embedding_pre["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_pre, y = word_pre_4, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_pre_4 <- df_umap_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_4, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

### (3) The Glove model for total Parliament speech after the 2008 economic crisis

```{r}
set.seed(42L)
glove_text_post <- sample(data_post$desc)

@@

```{r}
url_post <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_post.rds?raw=true"
golve_embedding_post <- readRDS(url(url_post, method = "libcurl"))
```

@@

Post-crisis total parliament speech word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylums)
word_post_3 <- glove_embedding_post["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_post, y = word_post_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_post_3 <- df_umap_post %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_3, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_4, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
set.seed(42L)
glove_text_conser_pre <- sample(data_conser_pre$desc)

@@

```{r, eval=FALSE}
url_conser_pre <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_conser_pre.rds?raw=true"
golve_embedding_conser_pre <- readRDS(url(url_conser_pre, method = "libcurl"))
```

@@

Pre-crisis Conservative party word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylums)
word_conser_pre_3 <- glove_embedding_conser_pre["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_conser_pre, y = word_conser_pre_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_conser_pre_3 <- df_umap_conser_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_3, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Pre-Crisis) word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
# Plot the word embedding of words that are related for the GloVe model (asylum)
word_conser_pre_4 <- glove_embedding_conser_pre["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_conser_pre, y = word_conser_pre_4, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_conser_pre_4 <- df_umap_conser_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_4, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Pre-Crisis) word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
set.seed(42L)
glove_text_conser_post <- sample(data_conser_post$desc)

@@

```{r}
url_conser_post <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_conser_post.rds?raw=true"
golve_embedding_conser_post <- readRDS(url(url_conser_post, method = "libcurl"))
```

@@

Post-crisis Conservative party word embedding of words related to *asylums*

```{r}
# Plot the word embedding of words that are related for the GloVe model (case3: asylums)
word_conser_post_3 <- glove_embedding_conser_post["asylums",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_conser_post, y = word_conser_post_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_conser_post_3 <- df_umap_conser_post %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_post_3, aes(x = Post_Cons1, y = Post_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_Cons1, Post_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Post-Crisis) word embedding of 'asylums'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case4: asylum)
word_conser_post_4 <- glove_embedding_conser_post["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_conser_post, y = word_conser_post_4, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_conser_post_4 <- df_umap_conser_post %>% 
  inner_join(y=select, by= "word")
```

@@

```{r}
set.seed(42L)
glove_text_labour_pre <- sample(data_labour_pre$desc)

@@

```{r}
url_labour_pre <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_labour_pre.rds?raw=true"
golve_embedding_labour_pre <- readRDS(url(url_labour_pre, method = "libcurl"))
```

@@

```{r}
set.seed(42L)
glove_text_labour_post <- sample(data_labour_post$desc)

@@

```{r}
url_labour_post <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_labour_post.rds?raw=true"
golve_embedding_labour_post <- readRDS(url(url_labour_post, method = "libcurl"))
```

@@

>>>>

---
title: "Draft_markdown_v1"
author: "River Kim"
date: "2024-04-07"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

@@

```{r}
# Packages
library(tidyverse)
library(readr)
library(tidytext)
library(quanteda)
library(textdata)
```

@@

# arrange the data by party and count the number of speech
tidy_data_notoken %>%
  group_by(party) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

@@

```{r}
# Plotting counts of immigration texts by party
ggplot(text_count, aes(x = Year, y = n, group = party, color = party)) +
  geom_line() +
  labs(y = "Immigration texts num", x = "Year") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(format(as.Date("2007-09-14"), "%Y")), col="red") +
  annotate("text", x = as.numeric(format(as.Date("2007-09-14"), "%Y")), y = 600, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 3)

@@

```{r}
#Plotting the ratios of immigration related texts 
ggplot(filtered_ratio_count, aes(x = Year, y = ratio, group = party, color = party)) +
  geom_line() +
  labs(y = "% Immigration Texts (n>100)", x = "Year") +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0), limits = c(0, NA)) +
  scale_x_continuous(breaks = seq(min(filtered_ratio_count$Year), max(filtered_ratio_count$Year), by = 4)) +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(format(as.Date("2007-09-14"), "%Y")), col="red") +
  annotate("text", x = as.numeric(format(as.Date("2007-09-14"), "%Y")), y = 0.04, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 3)
```

@@

tidy_data <- tidy_data %>%
  arrange(date)
tidy_data$order <- 1:nrow(tidy_data) # Make orders of each word

@@

# Make nrc sentiment tables of data
nrc_data <- tidy_data %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  count(date, sentiment) %>%
  spread(key = sentiment, value = n, fill = 0) %>%
  mutate(ratio = negative / (positive+1)) # Calculating negative/positive ratio. Adding 1 to avoid the 0 denominator

@@

```{r}
# Total sentiment of text including immigration related words plot (Using negative ratio)
nrc_data %>%
  ggplot(aes(date, ratio)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", alpha=0.5) +
  labs(y = "Total NRC sentiment negative ratio", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red") +
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
```
There is no time when particularly negative emotions are revealed. Rather, negative feelings toward immigrants are less visible after the financial crisis.

@@

```{r}
# A negative sentiment ratio plot of four parties
filtered_nrc_data_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.5, size = 1) +
  geom_smooth(method="loess", se = F, alpha=0.7, size = 1) +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y") +
  labs(y = "NRC Sentiment Negative Ratio by Party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col="red", size = 1) +
  annotate("text", x = as.Date("2007-09-24"), y = 4, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4) +
  theme_minimal() +
  theme(legend.position = "bottom")
```
Similar to the overall sentiment plot, there is no period when the proportion of negative words appears prominently.

@@

```{r}
# Faceting by party
filtered_nrc_data_party %>%
  ggplot(aes(x = date, y = ratio, color = party)) +
  geom_point(alpha = 0.5, size = 2) +
  geom_smooth(method = "loess", se = FALSE, alpha = 0.7, size = 1) +
  labs(y = "NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "none")
```
Similar to the overall sentiment plot, there is no period when the proportion of negative words appears prominently.

@@

show(dominant_senti_nrc_party)
```
The large number of sentiment counts is generated by the Conservatives and Labor parties.

@@

```{r}
# Plotting specific sentiment changes by party
long_nrc_data %>%
  ggplot(aes(x = date, y = score, color = sentiment)) +
  geom_smooth(method = "loess", se = F, alpha = 1, size = 1) +
  geom_point(alpha = 0.5, size = 0.5) + 
  facet_wrap(~ party, scales = "free_y") +
  labs(x = "Date", y = "Score") +
  theme_minimal() +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
The smooth line in each plot shows a relatively steady and unchanged shape.

@@

# Plots of specific negative sentiments by party 
long_nrc_data_neg %>%
  ggplot(aes(x = date, y = score, color = sentiment_negative)) +
  geom_smooth(method = "loess", se = F, alpha = 0.75, size = 1) +  
  geom_point(aes(shape = sentiment_negative), alpha = 0.5, size = 1) + 
  facet_wrap(~ party, scales = "free_y", nrow = 2) + 
  labs(x = "Date", y = "Score") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
Regarding negative sentiments, the Conservative party presents more diverse and fluctuated points than other parties. However, the general smooth lines stay steady.
## 5) Random sample sentiment

@@

# Applying NRC dictionary and calculating total negative ratio
samp_nrc_data <- tidy_samp %>%
  inner_join(get_sentiments("nrc"), by = "word") %>%
  count(date, sentiment) %>%
  spread(key = sentiment, value = n, fill = 0) %>%
  mutate(ratio = negative / (positive+1))

@@

```{r}
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess", se = F, alpha=0.25, size = 1.5) +
  labs(y = "Sample NRC sentiment negative ratio by party", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) + 
  annotate("text", x = as.Date("2007-09-24"), y = 5, label="Northern Rock\nLiquidity Support", angle=90, color = "black", size = 4)
  theme_minimal() +
  theme(legend.position = "bottom")
```
Negative sentiments of sample texts also show steady lines.

@@

```{r}
# Faceting plots by party
filtered_samp_nrc_party %>%
  ggplot(aes(date, ratio, color = party)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = F, alpha = 0.7, size = 1) +
  labs(y = "Sample NRC Sentiment Negative Ratio", x = "Date") +
  facet_wrap(~party, scales = "free_y") +  
  geom_vline(xintercept = as.numeric(as.Date("2007-09-14")), col = "red", size = 1) +
  theme_minimal() +
  theme(legend.position = "bottom")
```
Compared to the immigration related text sentiment plots, sample sentiment plots show no significant difference.

@@

```{r, eval=FALSE}
# choice parameters
WINDOW_SIZE <- 6 # context up to 6 words
DIM <- 300 # the length of the word vector
ITERS <- 100 # the maximum number of iterations
COUNT_MIN <- 10 # minimum count of words

@@

```{r, eval=FALSE}
#set model parameters
glove <- GlobalVectors$new(rank = DIM, x_max = 100, learning_rate = 0.05)

@@

Plot the total word embedding of 'immigration' with the GloVe model generated above.

@@

The ggplot visual for GloVe regarding total immigration related texts. Total parliament speech word embedding of words related to *immigration*

```{r}
ggplot(selected_words, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "GloVe word embedding of words related to 'immigration'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
I did it for confirming the modeling process, but we might need to use this map as a comparison plot.

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_2, aes(x = UMAP1, y = UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(UMAP1, UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Total parliament immigration related speech word embedding of 'immigrants'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
This can be also used for comparison. Also, word embedding maps tell us the general relationships between words, especially those we are interested in.

For the last pilot modelling map, there is a total parliament immigration related speech word embedding of words related to *asylum*

@@

```{r, eval=FALSE}
# filter data by date. Now have pre/post economic crisis text data related to immigration.

@@

```{r, eval=FALSE}
# repeat the same modeling process
set.seed(42L)
glove_text_pre <- sample(data_pre$desc)

@@

```{r}
url_pre <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_pre.rds?raw=true"
glove_embedding_pre <- readRDS(url(url_pre, method = "libcurl"))
```

Pre-crisis GloVe word embedding model of total parliament texts by two dimensional umap

@@

Let's see the whole word embedding map of two dimensions
```{r}
ggplot(df_umap_pre) +
  geom_point(aes(x = Pre_UMAP1, y = Pre_UMAP2), color = 'blue', size = 0.05) +
  labs(title = "(Pre-crisis) GloVe word embedding of words related to 'immigration'") +
  theme_minimal()
```

Specify the map. Which words are close to the word 'immigration' in the total parliament texts? Pre-crisis total parliament speech word embedding of words related to *immigration*

@@

@@

```{r}
# Plot the word embedding of words that are related for the GloVe model (asylum)
word_pre_3 <- glove_embedding_pre["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_pre, y = word_pre_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_pre_3 <- df_umap_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_pre_3, aes(x = Pre_UMAP1, y = Pre_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_UMAP1, Pre_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Pre-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

Now we can check the words relationships before the 2008 financail crisis.

### (3) The Glove model for total Parliament speech after the 2008 financial crisis

Again, same modeling process
```{r, eval=FALSE}
set.seed(42L)
glove_text_post <- sample(data_post$desc)

@@

```{r}
url_post <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_post.rds?raw=true"
glove_embedding_post <- readRDS(url(url_post, method = "libcurl"))
```

@@

@@

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_post_4, aes(x = Post_UMAP1, y = Post_UMAP2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Post_UMAP1, Post_UMAP2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "(Post-Crisis) total parliament speech word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```
We can now compare the two periods with three different embedding maps.

@@

```{r, eval=FALSE}
set.seed(42L)
glove_text_conser_pre <- sample(data_conser_pre$desc)

@@

```{r}
url_conser_pre <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_conser_pre.rds?raw=true"
glove_embedding_conser_pre <- readRDS(url(url_conser_pre, method = "libcurl"))
```

@@

@@

```{r}
# Plot the word embedding of words that are related for the GloVe model (case3: asylum)
word_conser_pre_3 <- glove_embedding_conser_pre["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_conser_pre, y = word_conser_pre_3, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_conser_pre_3 <- df_umap_conser_pre %>% 
  inner_join(y=select, by= "word")
```

```{r}
#The ggplot visual for GloVe
ggplot(selected_words_conser_pre_3, aes(x = Pre_Cons1, y = Pre_Cons2)) + 
  geom_point(show.legend = FALSE) + 
  geom_text(aes(Pre_Cons1, Pre_Cons2, label = word), show.legend = FALSE, size = 2.5, vjust=-1.5, hjust=0) +
  labs(title = "Conservative party (Pre-Crisis) word embedding of 'asylum'") +
  theme(plot.title = element_text(hjust = .5, size = 14))
```

@@

```{r, eval=FALSE}
set.seed(42L)
glove_text_conser_post <- sample(data_conser_post$desc)

@@

```{r}
url_conser_post <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_conser_post.rds?raw=true"
glove_embedding_conser_post <- readRDS(url(url_conser_post, method = "libcurl"))
```

@@

@@

```{r}
# Plot the word embedding of words that are related for the GloVe model (Case3: asylum)
word_conser_post_4 <- glove_embedding_conser_post["asylum",, drop = FALSE]
cos_sim = sim2(x = glove_embedding_conser_post, y = word_conser_post_4, method = "cosine", norm = "l2")
select <- data.frame(rownames(as.data.frame(head(sort(cos_sim[,1], decreasing = TRUE), 25))))
colnames(select) <- "word"
selected_words_conser_post_4 <- df_umap_conser_post %>% 
  inner_join(y=select, by= "word")
```

@@

```{r, eval=FALSE}
set.seed(42L)
glove_text_labour_pre <- sample(data_labour_pre$desc)

@@

```{r}
url_labour_pre <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_labour_pre.rds?raw=true"
glove_embedding_labour_pre <- readRDS(url(url_labour_pre, method = "libcurl"))
```

@@

```{r, eval=FALSE}
set.seed(42L)
glove_text_labour_post <- sample(data_labour_post$desc)

@@

```{r}
url_labour_post <- "https://github.com/RiverKim-garam/CTA24-Final-assessment/blob/main/local_glove_labour_post.rds?raw=true"
glove_embedding_labour_post <- readRDS(url(url_labour_post, method = "libcurl"))
```

@@

Now we made three different specific words (immigration, immigrants, asylum) GloVE embedding umap by party and the period. By comparing the connections of words, we can estimate the contexts how the words were used.

```{r}
# Instead of LaTex, use TinyTeX to knit the mark down result into pdf
library(tinytex)
```
